Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-03 article.tex
introduced LARS and explained what it is meant for and why it is not a suitable foundation for new approaches to stream reasoning

>>>>

  As such, until recently, stream reasoning either lacked a coherent semantics for continuous truth and entailment, or was necessarily a terminus rather than intermediate process in any streamed data pipeline.
  However, the work by \citet{LARS} has produced the LARS framework, by which the semantics of stream processing systems may be expressed and formally analysed.
  LARS extends the semantics of Answer Set Programming (itself an extension of Datalog semantics with features such as Negation as Failure) with the notion of streamed data with a point-in-time semantics.
  Paired with this is the notion of a logical windowing operator that supports the expression of windows as part of the general knowledge of a reasoning problem, as is necessary to express reasoning as performed by the iterative application of continuous queries in the manner already discussed.
  Though this form of windowing also allows the expression of temporally-aware rules in the manner of Complex Event Processing, it does \emph{not} align with or support the original intent of \emph{global windowing} in stream querying.
  Furthermore, the expression of granular windowing such as that expressible in LARS has not been defined in existing Semantic Web reasoning languages such as RIF \citep{w3crif} and OWL \citep{w3cowl2}.
  Finally, the complexity of entailment over programs as defined in LARS makes it unsuitable as a semantics on which to \emph{base} the expression of reasoning in real-time:
  the complexity of entailment in LARS is PSPACE, or co-NP given restrictions on window-nesting, where real-time processing of a task requires that task to be at most polynomial in its time complexity.
